>

### 2020-08-26 spinifex_RJpostProofing_20200824/spyrison-cook.Rmd
gifs and rmds for all pcs, not just figures. and their zip

## Saving gif for the supplementary material:
if (FALSE){
  play_manual_tour(basis = jet_bas, data = jet_dat, manip_var = jet_mvar,
                   color = jet_clas, shape = jet_clas,
                   ggtheme = list(theme_void(), theme(legend.position = "none")),
                   fps = 8, start_pause = .5, end_pause = 1,
                   render_type = render_gganimate,
                   gif_filename = "jetcluster_radialtour_pc4.gif", 
                   gif_path = "./gifs")
}

@@

## Saving gif for the supplementary material:
if (FALSE){
  play_manual_tour(basis = jet_bas, data = jet_dat, manip_var = jet_mvar,
                   color = jet_clas, shape = jet_clas,
                   ggtheme = list(theme_void(), theme(legend.position = "none")),
                   fps = 8, start_pause = .5, end_pause = 1,
                   render_type = render_gganimate,
                   gif_filename = "jetcluster_radialtour_pc3.gif", 
                   gif_path = "./gifs")
}
```

@@

## Saving gif for the supplementary material
if (FALSE){
  play_manual_tour(basis = DIS_bas, data = DIS_dat, manip_var = DIS_mvar,
                   color = DIS_clas, shape = DIS_clas,
                   ggtheme = list(theme_void(), theme(legend.position = "none")),
                   fps = 8, start_pause = .5, end_pause = 1,
                   render_type = render_gganimate,
                   gif_filename = "discluster_radialtour_pc6.gif", 
                   gif_path = "./gifs")
}

>>>>

## Saving gif of radial tour for each PC; for the supplementary material
if (FALSE){
  for(i in 1:ncol(jet_dat)){
    fn <- paste0("jetcluster_radialtour_pc", i, ".gif")
    play_manual_tour(basis = jet_bas, data = jet_dat, manip_var = i,
                     color = jet_clas, shape = jet_clas,
                     ggtheme = list(theme_void(), theme(legend.position = "none")),
                     fps = 8, start_pause = .5, end_pause = 1,
                     render_type = render_gganimate,
                     gif_filename = fn, 
                     gif_path = "./gifs")
  }
}

@@

## Figure
array2ggfacets(tour_array = jet_mtour, data = jet_dat,
               m_var = jet_mvar, class = jet_clas)
```

@@

## Saving gif of radial tour for each PC; for the supplementary material
if (FALSE){
  for(i in 1:ncol(DIS_dat)){
    fn <- paste0("discluster_radialtour_pc", i, ".gif")
    play_manual_tour(basis = DIS_bas, data = DIS_dat, manip_var = i,
                     color = DIS_clas, shape = DIS_clas,
                     ggtheme = list(theme_void(), theme(legend.position = "none")),
                     fps = 8, start_pause = .5, end_pause = 1,
                     render_type = render_gganimate,
                     gif_filename = fn, 
                     gif_path = "./gifs")
  }
}
